Computer Science House Constitution

### 2022-08-27 constitution.tex
Removes ability for RTP's to overide requirments

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns or changes membership status.

@@

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
	\item Public Relations Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairperson
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairperson and at least two-thirds of the Voting Members of the Executive Board must be present for the meeting to be called.

@@

\asubsection{Responsibilities of the Public Relations Director}
\begin{enumerate}
	\item To preside over Public Relations Directorship Meetings
	\item To operate House social media accounts intended to represent House as a whole
	\item To oversee the organization, initiation, and execution of House philanthropic events
	\item To preserve and improve the public image of House
	\item To collaborate with other Executive Board members to organize, initiate, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members

@@

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Public Relations & 5\% \\
\hline
Accumulated & 5\% \\
\hline
\end{tabular}
\end{center}

@@

\asubsubsection{Evaluations Processes}
During the academic year, a House member is evaluated by the Membership Evaluation.
The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
Semi-Annual Evaluations Meetings are open only to current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\\* \\*
At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
\asubsubsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year.
It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

@@

\asubsubsection{Qualifications of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
	\item Candidates may be granted an exemption by current Root Type Persons.
		Such an exemption may be withdrawn at any time by the current Root Type Persons.
	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
\end{enumerate}

@@

\asection{Qualifications}
\asubsection{Qualifications to be the Chairperson, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must reside on floor during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director, Public Relations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
\end{enumerate}

@@

\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s), Public Relations Director}

@@

% ARTICLE VII - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}

>>>>

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Qualifying members may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for vote at the next Evaluations meeting.
If a majority is in favor of the return, the Alumni is reinstated as an Active Member with Off-Floor status effective immediately.
The decision will be announced at the following House meeting.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the right to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated semi-annually through the Evaluation Process as described in \ref{Evaluations Processes}.
Failure of the Evaluation Process could result in the member being asked to find alternative housing as soon as possible in accordance with all applicable Residence Life policies regarding room changes.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member: resigns or changes membership status.

@@

% ARTICLE V - EXECUTIVE BOARD
\article{Executive Board}
The Executive Board is the main governing body of the House.
Its purpose is to provide leadership and direction for the House, to oversee the day-to-day operations of the House, and to initiate and organize programs and projects for the House.
It is composed of the seven permanent directors and the Chairperson.
\\*\\*
There is one permanent directorship for each major aspect of the government of the House and each one is chaired by an Executive Board member.
Ad Hoc directorships are created on an as-needed basis.
They are generally very task oriented and are chaired by a House member.
A directorship has some jurisdiction in its area of interest and often is responsible for the day-to-day decisions regarding its area of interest.
Any large expenditures or large effect decisions must be brought before the entire House
\asection{Members of the Executive Board}
\asubsection{Voting Members}
\begin{itemize}
	\item Evaluations Director
	\item Social Director(s)
	\item Financial Director
	\item Research and Development Director(s)
	\item House Improvements Director
	\item Operational Communications Director
	\item House History Director
\end{itemize}
\asubsection{Non-Voting Members}
\begin{itemize}
	\item Chairperson
	\item House Secretary
	\item Ad Hoc Director(s)
\end{itemize}
\asection{Closed Executive Board}
Closed Executive Board Meetings are open only to the Chairperson, Voting Members of the Executive Board, and those with the express permission of the Executive Board.
A closed Executive Board meeting may be called at any time by any member of the Executive Board.
However, the Chairperson and at least two-thirds of the Voting Members must be present for the meeting to be called.

@@

@@

\asection{Operations}
\asubsection{Operations of the Financial Directorship}
\asubsubsection{Amount of House Dues}
The amount of dues for Active Members will be eighty dollars (\$80.00) per Academic Semester.
\asubsubsection{Collection of House Dues}
The collection period of house dues will be decided in conjunction with The Center for Residence Life and Housing Operations.
During the dues collection period, dues for on-floor members (for both semesters) are collected through the member’s RIT bill.
Dues for off-floor members are to be collected during this period as well by the Financial Director.
For any member who moves on or off-floor during the year, any difference between dues paid and dues owed should be collected.
Dues for any alumnus/alumnae in good standing are to be collected when intention to pay is expressed to the Financial Director.
\asubsubsubsection{Rules for Giving Exceptions and Exemptions for House Dues}
If a member is unable to pay dues upon request, they may appeal their situation to the Financial Director.
If the Financial Director deems their situation appropriate, they may grant specific extensions or reductions of the member's payment as they see fit.
If the Financial Director deems their situation inappropriate for extension, the member may appeal to the Executive Board.
If the Executive Board disagrees with the Financial Director, the Executive Board may reduce the required payment or extend the payment deadline.
If the Executive Board agrees with the Financial director, the member’s payment is considered delinquent and the member’s privileges are revoked until payment can be made.
In the case the Financial Director or Executive Board decides the situation is appropriate, the member's dues may be partially or fully excused, or the member may be given additional time to pay their dues. 
Additional time and reduction of dues may both be given to a member in an appropriate situation.
All dues must be collected in full before the annual membership evaluation (\ref{Membership Evaluation}).
After this date, dues collection is suspended until the start of the next academic year.
\asubsubsection{Breakdown of Dues for Directorship Budgets}
\begin{center}
\begin{tabular}[c]{|l c|}
\hline
Directorship Name & Percentage of Dues \\
\hline
\hline
Operational Communications & 20\% \\
\hline
Evaluations \& Selections & 5\% \\
\hline
House History & 10\% \\
\hline
House Improvements & 15\% \\
\hline
Research and Development & 20\% \\
\hline
Social & 20\% \\
\hline
Accumulated & 10\% \\
\hline
\end{tabular}
\end{center}

@@

\asubsubsection{Evaluations Processes}
During the academic year, a House member is evaluated by the Membership Evaluation.
The Membership Evaluation is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
Semi-Annual Evaluations Meetings are open only to current Active Members.
All Executive Board members are expected to attend the Semi-Annual Evaluations Meetings to assist in the evaluations of House members.
\\* \\*
At the beginning of any Evaluation Process listed herein, the Evaluations Director must read the sections of the Computer Science House Constitution and By-Laws used during the respective Evaluation Process.
It is incumbent upon each House member to provide the Evaluation Director with whatever information they feel is necessary to ensure an accurate evaluation.
\asubsubsubsection{Membership Evaluation}
The Membership Evaluation process occurs once per academic year.
It is performed as part of the Evaluation Process that takes place during the spring semester to comply with RIT Housing deadlines.
\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of House Members} at the beginning of the Membership Evaluation passes their Membership Evaluation without being voted on or evaluated by the quorum.
All Active Members who have not recieved an exemption from the Executive Board prior to the Membership Evaluation will be evaluated on a Member by Member basis by a quorum of Active Members.
The Membership Evaluation shall hold members to the objective requirements defined in \ref{Expectations of House Members} and determine which members may continue as an Active Member in the following Standard Operating Session.
Exceptions to the requirements may be made, as House may choose any of the Outcomes for each Member, even if the Member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Evaluation occurs.
A Secret Immediate Simple Majority vote with a Quorum of two-thirds of the Total Number of Possible Votes is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

@@

\asubsubsection{Qualifications of a Root Type Person}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\begin{enumerate}
	\item Candidates must have been an On-Floor Active Member in good standing within the last twelve months, or been an Off-Floor Active Member and have lived on the floor within the last twelve months.
	\item Prior Root Type Persons are those members who are no longer current Active Members and have not been granted an extension by the current Root Type Persons.
		Prior Root Type Persons are not guaranteed access to the current root passwords and other authentication tokens.
	\item The current Root Type Persons may from time to time draft rules and regulations specifying the rights and privileges of Prior Root Type Persons.
\end{enumerate}

@@

\asection{Qualifications}
\asubsection{Qualifications to be the Chairperson, Evaluations Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must reside on floor during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold a simultaneous voting Executive Board position, and must therefore resign their current position, or the position of Chairperson, should they be elected
\end{enumerate}
\asubsection{Qualifications to be the Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office
	\item Candidates must have at least one full semester of House membership as an Active Member
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}.
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other voting Executive Board Position.
\end{enumerate}

@@

\asubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, House History Director, Research and Development Director(s)}

@@

% ARTICLE VII - JUDICIAL
\article{Judicial}
The Executive Board may approve (by simple majority) a request (from a member) for a Judicial proceeding when an official clarification of the Constitution or By-Laws is required, there is a conflict among House Members, or a House interest needs resolution.
\asection{Formation of a Judicial Board}
A Judicial Board is made up of the Chairperson, the Evaluations director, and an additional voting member of the Executive Board chosen by a majority vote among the Executive Board.
If either the Chairperson or Evaluations Director are deemed biased or unfit for a position on the Judicial Board, they will be replaced by another voting member of the Executive Board by means of a simple majority vote amongst the remaining Executive Board members.
\asection{Judicial Investigation}
The Judicial Board will be responsible for making all necessary inquiries into the matter of the request brought to the Judicial Board.
\asection{Judicial Ruling}
The Judicial Board may present an official ruling following the Judicial Investigation.
This ruling may be appealed in the same manner as an Executive Board decision \ref{Appeals}.
\end{document}
